Final Report Semester Project

### 2018-12-06 Visualizations/Draft Visualizations Template.Rmd
Added note at beginning, summary placeholder, and my contribution

---
title: "Draft Visualizations for Semester Project"
output:
  word_document: default
---

@@

@@

>>>>

---
title: "Final Report Semester Project"
output:
  word_document: default
---

@@

#Introduction

This document contains the fully commented analysis script and outputs, written summary of the project, and summary of contributorship to each part of the project.

@@

#Summary

This is a placeholder for the summary.

#Who did what in the project

Laura - For the work plan, I worked with the group to draft the sections on dataset used, audience, and research questions. I also reviewed a list of studies on mental health in the workplace and drafted summaries that can be used as a reference by the group. For the data cleaning documentation, I examined nine variables and noted if there were any issues. I worked with other group members to determine how to handle the variables. For the R Script, I did frequency tables related to my analyses and the variables I examined for data cleaning.  For the R Plot Draft, I created visualizations and interpretations for my analyses (in section 3, the portions on anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors). For the presentation, I created a template for the presentation that included what was needed and placeholder slides for the analyses the group did. I also did slides related to my analysis (anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors) and used the findings to draft some recommendations.For the final package, I did the first draft of the summary.
